\bf Title here

### 2020-06-24 paper/paper.Rmd
rearrange the structure of the paper as agreed in the meeting: design and plots go tgt

# Visual diagnostic in guided tour {#apply}

In this section, we present the simulated data along with how the global object can be applied in guided tour.

@@

## Simulated data

@@

# Diagnostics plots {#plots}

@@

## Explore the value of objective function {#static}

### Toy example: exploring searching points

@@

### A more complex example: adding an interruption in the interpolation stage

@@

### Another example: polishing the final projection basis

@@

## Explore searching space {#animated}

@@

### A toy example: understand different stage of search_geodesic

@@

### A more complex example: Choosing the initial value for polishing parameter

@@

## A comprehensive example of diagnosing a noisy index function

@@

# Vis package

Everything is coded up in a package.

>>>>

@@

### Simulated data

@@

@@

### Explore the value of objective function {#static}

#### Toy example: exploring searching points

@@

#### A more complex example: adding an interruption in the interpolation stage

@@

#### Another example: polishing the final projection basis

@@

### Explore searching space {#animated}

@@

#### A toy example: understand different stage of search_geodesic

@@

#### A more complex example: Choosing the initial value for polishing parameter

@@

### A comprehensive example of diagnosing a noisy index function

@@

# Implementation: Ferrn pacakge

Everything is coded up in a package. Package structure

# Conclusion

### 2020-06-24 paper/paper.tex
rearrange the structure of the paper as agreed in the meeting: design and plots go tgt

\hypertarget{apply}{%
\section{Visual diagnostic in guided tour}\label{apply}}

In this section, we present the simulated data along with how the global
object can be applied in guided tour.

\hypertarget{global-object-1}{%
\subsection{Global object}\label{global-object-1}}

@@

\hypertarget{simulated-data}{%
\subsection{Simulated data}\label{simulated-data}}

@@

\hypertarget{plots}{%
\section{Diagnostics plots}\label{plots}}

@@

\hypertarget{static}{%
\subsection{Explore the value of objective function}\label{static}}

\hypertarget{toy-example-exploring-searching-points}{%
\subsubsection{Toy example: exploring searching
points}\label{toy-example-exploring-searching-points}}

@@

\hypertarget{a-more-complex-example-adding-an-interruption-in-the-interpolation-stage}{%
\subsubsection{A more complex example: adding an interruption in the
interpolation
stage}\label{a-more-complex-example-adding-an-interruption-in-the-interpolation-stage}}

@@

\hypertarget{another-example-polishing-the-final-projection-basis}{%
\subsubsection{Another example: polishing the final projection
basis}\label{another-example-polishing-the-final-projection-basis}}

@@

\hypertarget{animated}{%
\subsection{Explore searching space}\label{animated}}

@@

\hypertarget{a-toy-example-understand-different-stage-of-search_geodesic}{%
\subsubsection{A toy example: understand different stage of
search\_geodesic}\label{a-toy-example-understand-different-stage-of-search_geodesic}}

@@

\hypertarget{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}{%
\subsubsection{A more complex example: Choosing the initial value for
polishing
parameter}\label{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}}

@@

\hypertarget{a-comprehensive-example-of-diagnosing-noisy-index-function}{%
\subsection{A comprehensive example of diagnosing noisy index
function}\label{a-comprehensive-example-of-diagnosing-noisy-index-function}}

@@

\hypertarget{vis-package}{%
\section{Vis package}\label{vis-package}}

Everything is coded up in a package.

>>>>

@@

\hypertarget{simulated-data}{%
\subsubsection{Simulated data}\label{simulated-data}}

@@

@@

\hypertarget{static}{%
\subsubsection{Explore the value of objective function}\label{static}}

\hypertarget{toy-example-exploring-searching-points}{%
\paragraph{Toy example: exploring searching
points}\label{toy-example-exploring-searching-points}}

@@

\hypertarget{a-more-complex-example-adding-an-interruption-in-the-interpolation-stage}{%
\paragraph{A more complex example: adding an interruption in the
interpolation
stage}\label{a-more-complex-example-adding-an-interruption-in-the-interpolation-stage}}

@@

\hypertarget{another-example-polishing-the-final-projection-basis}{%
\paragraph{Another example: polishing the final projection
basis}\label{another-example-polishing-the-final-projection-basis}}

@@

\hypertarget{animated}{%
\subsubsection{Explore searching space}\label{animated}}

@@

\hypertarget{a-toy-example-understand-different-stage-of-search_geodesic}{%
\paragraph{A toy example: understand different stage of
search\_geodesic}\label{a-toy-example-understand-different-stage-of-search_geodesic}}

@@

\hypertarget{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}{%
\paragraph{A more complex example: Choosing the initial value for
polishing
parameter}\label{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}}

@@

\hypertarget{a-comprehensive-example-of-diagnosing-a-noisy-index-function}{%
\subsubsection{A comprehensive example of diagnosing a noisy index
function}\label{a-comprehensive-example-of-diagnosing-a-noisy-index-function}}

@@

\hypertarget{implementation-ferrn-pacakge}{%
\section{Implementation: Ferrn
pacakge}\label{implementation-ferrn-pacakge}}

Everything is coded up in a package. Package structure

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}
